---
title: "Case 1: Natural-language plotting"
subtitle: "自然语言作图"
output:
  html_document:
    toc: true
    toc_depth: 2
params:
  run_live: false
  output_dir: "outputs"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 7.5,
  fig.height = 5
)

pkg_root <- normalizePath(file.path(getwd(), "..", ".."), mustWork = FALSE)
if (!file.exists(file.path(pkg_root, "DESCRIPTION"))) {
  pkg_root <- normalizePath(getwd(), mustWork = FALSE)
}
if (requireNamespace("pkgload", quietly = TRUE) && file.exists(file.path(pkg_root, "DESCRIPTION"))) {
  aisdk_path <- Sys.getenv("GGAI_AISDK_PATH", "/Users/xiayh/Projects/aisdk")
  if (dir.exists(aisdk_path)) {
    try(pkgload::load_all(aisdk_path, export_all = FALSE, helpers = FALSE, quiet = TRUE), silent = TRUE)
  }
  pkgload::load_all(pkg_root, export_all = FALSE, helpers = FALSE, quiet = TRUE)
}

library(ggplot2)
library(ggai)

dir.create(params$output_dir, recursive = TRUE, showWarnings = FALSE)
run_live <- isTRUE(params$run_live)
```

## Scenario

Use `ggai()` as a natural-language entry point: the user names a data object in
the prompt and asks for a chart in plain language.

This scenario is useful when the chart should remain an editable `ggplot`
session, but the first draft can be described conversationally.

```{r data}
car_data <- transform(
  mtcars,
  cylinders = factor(cyl),
  car = rownames(mtcars)
)

str(car_data[, c("mpg", "wt", "cylinders", "hp")])
```

## Offline reference

This is the chart the live prompt should be able to produce.

```{r offline-reference}
p_reference <- ggplot(car_data, aes(wt, mpg, colour = cylinders)) +
  geom_point(size = 3, alpha = 0.9) +
  scale_colour_brewer(palette = "Set2") +
  labs(
    title = "Fuel efficiency falls as vehicle weight increases",
    subtitle = "Reference chart grounded in mtcars",
    x = "Weight",
    y = "Miles per gallon",
    colour = "Cylinders"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")

p_reference
```

## Live ggai case

Set `params$run_live` to `true` to exercise the model-backed path.

```{r live-ggai, eval=params$run_live}
s <- ggai(
  "@car_data show fuel efficiency vs weight, color by cylinders. Keep it as an editable session."
)

plot(s)
session_context(s)
spec_history(s)
```

## Expected checks

```{r checks}
stopifnot(inherits(p_reference, "ggplot"))
if (run_live) {
  stopifnot(inherits(s, "ggai_session"))
}
```
