---
title: "Case 2: Existing ggplot augmentation"
subtitle: "增强已有 ggplot"
output:
  html_document:
    toc: true
    toc_depth: 2
params:
  run_live: false
  output_dir: "outputs"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 7.5, fig.height = 5)

pkg_root <- normalizePath(file.path(getwd(), "..", ".."), mustWork = FALSE)
if (!file.exists(file.path(pkg_root, "DESCRIPTION"))) {
  pkg_root <- normalizePath(getwd(), mustWork = FALSE)
}
if (requireNamespace("pkgload", quietly = TRUE) && file.exists(file.path(pkg_root, "DESCRIPTION"))) {
  aisdk_path <- Sys.getenv("GGAI_AISDK_PATH", "/Users/xiayh/Projects/aisdk")
  if (dir.exists(aisdk_path)) {
    try(pkgload::load_all(aisdk_path, export_all = FALSE, helpers = FALSE, quiet = TRUE), silent = TRUE)
  }
  pkgload::load_all(pkg_root, export_all = FALSE, helpers = FALSE, quiet = TRUE)
}

library(ggplot2)
library(ggai)

dir.create(params$output_dir, recursive = TRUE, showWarnings = FALSE)
run_live <- isTRUE(params$run_live)
```

## Scenario

Use `geom_ai()` when the analyst already has a correct `ggplot`, and only wants
AI-compiled communication layers: callouts, emphasis, labels, or additive
annotations.

The important boundary is that `ggplot` remains the statistical graphics
engine.

```{r base-plot}
car_data <- transform(mtcars, cylinders = factor(cyl), car = rownames(mtcars))

base_plot <- ggplot(car_data, aes(wt, mpg, colour = cylinders)) +
  geom_point(size = 3, alpha = 0.9) +
  scale_colour_brewer(palette = "Set2") +
  labs(
    title = "Fuel efficiency vs vehicle weight",
    x = "Weight",
    y = "Miles per gallon",
    colour = "Cylinders"
  ) +
  theme_minimal(base_size = 12)

base_plot
```

## Offline reference

This hand-written reference shows the intended augmentation style.

```{r offline-reference}
outlier <- car_data[which.max(car_data$wt - car_data$mpg / 10), ]
efficient <- car_data[which.max(car_data$mpg), ]

p_reference <- base_plot +
  annotate(
    "label",
    x = outlier$wt,
    y = outlier$mpg,
    label = "heavy / low MPG",
    hjust = 1.05,
    vjust = -0.4,
    size = 3.3,
    colour = "#4B5563",
    fill = "white",
    label.size = 0.25
  ) +
  annotate(
    "curve",
    x = outlier$wt - 0.6,
    y = outlier$mpg + 4,
    xend = outlier$wt,
    yend = outlier$mpg,
    curvature = -0.2,
    arrow = arrow(length = unit(0.12, "in")),
    colour = "#4B5563"
  ) +
  annotate(
    "text",
    x = efficient$wt + 0.35,
    y = efficient$mpg,
    label = "light efficient cluster",
    hjust = 0,
    size = 3.4,
    colour = "#0F766E"
  )

p_reference
```

## Live ggai case

```{r live-geom-ai, eval=params$run_live}
augmented <- base_plot +
  geom_ai(
    "Highlight the heavy low-MPG outlier, annotate the light high-efficiency cluster, and keep the result additive."
  )

augmented
inspect_spec(augmented)
as_code(augmented)
spec_history(augmented)
```

## Expected checks

```{r checks}
stopifnot(inherits(base_plot, "ggplot"))
stopifnot(inherits(p_reference, "ggplot"))
if (run_live) {
  stopifnot(inherits(augmented, "ggplot"))
}
```
