---
title: "Case 4: Reference figure adaptation"
subtitle: "参考图适配"
output:
  html_document:
    toc: true
    toc_depth: 2
params:
  run_live: false
  output_dir: "outputs"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 4.8)

pkg_root <- normalizePath(file.path(getwd(), "..", ".."), mustWork = FALSE)
if (!file.exists(file.path(pkg_root, "DESCRIPTION"))) {
  pkg_root <- normalizePath(getwd(), mustWork = FALSE)
}
if (requireNamespace("pkgload", quietly = TRUE) && file.exists(file.path(pkg_root, "DESCRIPTION"))) {
  aisdk_path <- Sys.getenv("GGAI_AISDK_PATH", "/Users/xiayh/Projects/aisdk")
  if (dir.exists(aisdk_path)) {
    try(pkgload::load_all(aisdk_path, export_all = FALSE, helpers = FALSE, quiet = TRUE), silent = TRUE)
  }
  pkgload::load_all(pkg_root, export_all = FALSE, helpers = FALSE, quiet = TRUE)
}

library(ggplot2)
library(ggai)

dir.create(params$output_dir, recursive = TRUE, showWarnings = FALSE)
run_live <- isTRUE(params$run_live)
```

## Scenario

Use reference adaptation when a user says: "make a plot like this paper figure"
or "use this screenshot's structure with my data."

The reference can supply structure or style, but the plotted values should come
from the user's data.

```{r data}
car_data <- transform(
  mtcars,
  cylinders = factor(cyl),
  transmission = factor(am, labels = c("Automatic", "Manual")),
  car = rownames(mtcars)
)

head(car_data[, c("mpg", "wt", "hp", "cylinders", "transmission")])
```

## Reference brief

For this runnable case, the "reference figure" is a short brief rather than an
external image:

- two panels split by transmission;
- scatter plot with direct trend lines;
- restrained palette;
- short callout for the highest-efficiency car.

```{r offline-reference-adaptation}
top_efficiency <- car_data[which.max(car_data$mpg), ]

p_reference_adapted <- ggplot(car_data, aes(wt, mpg, colour = cylinders)) +
  geom_point(size = 2.8, alpha = 0.85) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.7) +
  facet_wrap(~transmission) +
  scale_colour_brewer(palette = "Set2") +
  annotate(
    "label",
    x = top_efficiency$wt,
    y = top_efficiency$mpg,
    label = "highest MPG",
    size = 3,
    fill = "white",
    colour = "#374151",
    label.size = 0.25
  ) +
  labs(
    title = "Reference-style adaptation using user data",
    subtitle = "Structure and style are borrowed; values remain mtcars",
    x = "Weight",
    y = "Miles per gallon",
    colour = "Cylinders",
    caption = "Reference role: structure + style, not extracted source values."
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")

p_reference_adapted
```

## Live ggai case

```{r live-reference-adaptation, eval=params$run_live}
s <- ggai(
  paste(
    "@car_data make a reference-style two-panel figure.",
    "Borrow this structure: split by transmission, scatter mpg vs weight,",
    "add trend lines, use a restrained palette, and label the highest-efficiency car.",
    "Use mtcars values only and add a source note."
  )
)

plot(s)
session_context(s)
```

## Expected checks

```{r checks}
stopifnot(inherits(p_reference_adapted, "ggplot"))
if (run_live) {
  stopifnot(inherits(s, "ggai_session"))
}
```
