---
title: "Case 5: Final polish and explainer graphics"
subtitle: "最终润色与解释图"
output:
  html_document:
    toc: true
    toc_depth: 2
params:
  run_live: false
  output_dir: "outputs"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 7.5, fig.height = 5)

pkg_root <- normalizePath(file.path(getwd(), "..", ".."), mustWork = FALSE)
if (!file.exists(file.path(pkg_root, "DESCRIPTION"))) {
  pkg_root <- normalizePath(getwd(), mustWork = FALSE)
}
if (requireNamespace("pkgload", quietly = TRUE) && file.exists(file.path(pkg_root, "DESCRIPTION"))) {
  aisdk_path <- Sys.getenv("GGAI_AISDK_PATH", "/Users/xiayh/Projects/aisdk")
  if (dir.exists(aisdk_path)) {
    try(pkgload::load_all(aisdk_path, export_all = FALSE, helpers = FALSE, quiet = TRUE), silent = TRUE)
  }
  pkgload::load_all(pkg_root, export_all = FALSE, helpers = FALSE, quiet = TRUE)
}

library(ggplot2)
library(ggai)

dir.create(params$output_dir, recursive = TRUE, showWarnings = FALSE)
run_live <- isTRUE(params$run_live)
```

## Scenario

Use polish mode when the analytical chart is structurally correct and the next
need is communication finish: publication-style redraw, plot-reader callouts,
infographic board, or story figure.

This case creates the reference bundle offline. The live image-edit call is
optional because it uses an image model.

```{r base-plot}
car_data <- transform(mtcars, cylinders = factor(cyl), car = rownames(mtcars))

base_plot <- ggplot(car_data, aes(wt, mpg, colour = cylinders)) +
  geom_point(size = 3.2, alpha = 0.9) +
  scale_colour_brewer(palette = "Set2") +
  labs(
    title = "Fuel efficiency vs weight",
    subtitle = "Grounded chart before image-level polish",
    x = "Weight",
    y = "Miles per gallon",
    colour = "Cylinders"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom")

s <- start_ggai_session(base_plot)
plot(s)
```

## Offline polish bundle

`prepare_polish_bundle()` writes the base plot, geometry overlay, layout
overlay, layered redraw manifest, and prompt. This lets you inspect the
contract before any image model is called.

```{r polish-bundle}
bundle <- prepare_polish_bundle(
  s,
  instruction = paste(
    "Redraw this as a polished scientific explainer.",
    "Keep the data relationship faithful, improve typography and hierarchy,",
    "and add light plot-reader callouts."
  ),
  output_dir = params$output_dir,
  prefix = "case05_polish",
  width = 1400,
  height = 900
)

bundle$base_plot_path
bundle$geometry_overlay_path
bundle$layout_overlay_path
bundle$manifest_path
bundle$prompt_path
```

## Layer contract

The image mode now records a ggplot-native layer contract. It uses the same
mental model ggplot users already understand: theme surface, data geoms/stats,
scales and guides, labels and annotations, then communication polish.

```{r layer-contract}
bundle$manifest$layer_mode
bundle$manifest$layer_manifest$ordering

source_layers <- data.frame(
  order = vapply(bundle$manifest$layer_manifest$ggplot_reference_layers, `[[`, integer(1), "order"),
  role = vapply(bundle$manifest$layer_manifest$ggplot_reference_layers, `[[`, character(1), "role"),
  file = basename(vapply(bundle$manifest$layer_manifest$ggplot_reference_layers, `[[`, character(1), "file"))
)
source_layers

target_roles <- data.frame(
  order = vapply(bundle$manifest$layer_manifest$ggplot_output_roles, `[[`, integer(1), "order"),
  role = vapply(bundle$manifest$layer_manifest$ggplot_output_roles, `[[`, character(1), "role"),
  name = vapply(bundle$manifest$layer_manifest$ggplot_output_roles, `[[`, character(1), "name")
)
target_roles
```

```{r show-bundle-image, out.width='100%'}
knitr::include_graphics(bundle$base_plot_path)
```

## Live ggai image polish

```{r live-polish, eval=params$run_live}
image_model <- paste0("openai:", Sys.getenv("OPENAI_IMAGE_MODEL", "gpt-image-2"))

res <- gg_edit(
  s,
  "Redraw this as a polished scientific explainer with cleaner hierarchy and light numbered callouts.",
  mode = "polish",
  image_model = image_model,
  output_dir = params$output_dir,
  prefix = "case05_live_polish",
  width = 1400,
  height = 900,
  total_timeout_seconds = 900,
  first_byte_timeout_seconds = 180,
  connect_timeout_seconds = 15,
  idle_timeout_seconds = 300
)

res$best$path
plot(res)
artifacts(res$session)
```

## Expected checks

```{r checks}
stopifnot(inherits(bundle, "ggai_figure_polish_bundle"))
stopifnot(file.exists(bundle$manifest_path))
stopifnot(file.exists(bundle$prompt_path))
manifest_check <- jsonlite::read_json(bundle$manifest_path, simplifyVector = FALSE)
stopifnot(identical(manifest_check$layer_manifest$ordering, "bottom_to_top"))
if (run_live) {
  stopifnot(inherits(res, "ggai_polished_figure_result"))
}
```
